Learning constraints in tabular data

### 2016-05-10 Paper/ECAI/tabular.tex
Use S for templates

The inverse problem is, given an assignment to all cells, to find the constraints that are present in the spreadsheet.
We define the {\bf Tabular Constraint Learning Problem} as follows:
%
\begin{definition} \textit{Tabular Constraint Learning.}\label{def:problem_statement}
  Given ${\cal G}$ a set of groups derived from fully instantiated tables ${\cal T}$ (all cells have values) and a set of {\template}s ${\cal C}$ ; find the set of all constraints $s(G_1', ..., G_n')$ that match the syntax of a \template in ${\cal C}$ and where the groups $G_1', ... , G_n'$ with $\forall i, G_i' \subseteq G_i, G_i \in {\cal G}$ satisfy both the signature and the definition of that \template.
\end{definition}
% {\bf Given }
% \begin{enumerate}
% \item
% a set of instantiated tables (so all cells have values) ${\cal T}$;
% \item
% a set of {\template}s ${\cal C}$;
% \item
% a set of groups ${\cal G}$ for the tables ${\cal T}$;
% \end{enumerate}
% \noindent
% {\bf Find}  the set of all constraints $s(G_1', ..., G_n')$ that 
% \begin{enumerate}
% \item are satisfied  in ${\cal T}$;
% \item for which all $G_i' \subseteq G_i \in {\cal G}$ ;
% \item the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$.
% \end{enumerate}
An example solution for the type-consistent groups of the tables in Figure~\ref{fig:main_example} and {\template}'s in Table~\ref{table:constraints} is shown in Figure~\ref{fig:sol_example}.

>>>>

The inverse problem is, given an assignment to all cells, to find the constraints that are present in the spreadsheet.
We define the {\bf Tabular Constraint Learning Problem} as follows:
%
\begin{definition} \textit{Tabular Constraint Learning.}\label{def:problem_statement}
  Given ${\cal G}$ a set of groups derived from fully instantiated tables ${\cal T}$ (all cells have values) and a set of {\template}s ${\cal S}$ ; find the set of all constraints $s(G_1', ..., G_n')$ that match the syntax of a \template~$s \in {\cal S}$ and where the groups $G_1', ... , G_n'$ with $\forall i, G_i' \subseteq G_i, G_i \in {\cal G}$ satisfy both the signature and the definition of that \template.
\end{definition}
% {\bf Given }
% \begin{enumerate}
% \item
% a set of instantiated tables (so all cells have values) ${\cal T}$;
% \item
% a set of {\template}s ${\cal C}$;
% \item
% a set of groups ${\cal G}$ for the tables ${\cal T}$;
% \end{enumerate}
% \noindent
% {\bf Find}  the set of all constraints $s(G_1', ..., G_n')$ that 
% \begin{enumerate}
% \item are satisfied  in ${\cal T}$;
% \item for which all $G_i' \subseteq G_i \in {\cal G}$ ;
% \item the groups $G_1', ... , G_n'$ satisfy the signature of the constraint template~$s \in {\cal C}$.
% \end{enumerate}
An example solution for the type-consistent groups of the tables in Figure~\ref{fig:main_example} and {\template}'s in Table~\ref{table:constraints} is shown in Figure~\ref{fig:sol_example}.
